---
title: "R Programming-caching potentially time-consuming computations"
author: "Anita Lin"
date: "Saturday, February 14, 2015"
output: html_document
---

#Introduction

This second programming assignment will require you to write an R function is able to cache potentially time-consuming computations. For example, taking the mean of a numeric vector is typically a fast operation. However, for a very long vector, it may take too long to compute the mean, especially if it has to be computed repeatedly (e.g. in a loop). If the contents of a vector are not changing, it may make sense to cache the value of the mean so that when we need it again, it can be looked up in the cache rather than recomputed. In this Programming Assignment will take advantage of the scoping rules of the R language and how they can be manipulated to preserve state inside of an R object.


#Two functions for preparation

makeCacheMatrix: This function creates a special "matrix" object that can cache its inverse.
makeCacheMatrix creates a list containing a function to
1. set the value of the matrix
2. get the value of the matrix
3. set the value of inverse of the matrix
4. get the value of inverse of the matrix

```{r,results='hide'}

makeCacheMatrix <- function(x = numeric()) {
  i <- NULL
  set <- function(y) {
    x <<- y
    i  <<- NULL
  }
  get <- function() x
  setinverse <- function(inverse) i <<- inverse 
  getinverse <- function() i
  list(set = set, get = get,
       setinverse  = setinverse ,
       getinverse  = getinverse )
}

```


cachemean: returns the inverse of the matrix. Checking if getinverse can get the data firstly.If not, it will return an error message; otherwise, it will proceed the inverse.

```{r,results='hide'}

cacheSolve <- function(x, ...) {
  i <- x$getinverse()
  if(!is.null(i)) {
    message("getting cached data.")
    return(i)
  }
  data <- x$get()
  i <- solve(data)
  x$setinverse(i)
  i
}
```

However, I save these two function in my local driver and called time_consuming.R.


#Start to run
Call the function
```{r}
source("time_consuming.R")
```

Create the matrix and list row data
```{r}
source("time_consuming.R")
data<- rbind(c(1, 2), c(2, 1))
data;
```

Check the inverse matrix fistly.
```{r}
solve(data)
```

Run the makeCacheMatrix function to creates a special "matrix" object that can cache its inverse
```{r}
f<-makeCacheMatrix(data)
```


Check if get is able to display the data.
```{r}
f$get();
```

Run cachemean fucntion to calculate the mean and return the value to makeVctor function
```{r}
cacheSolve(f)
```


Check if using getinverse function is albe to display the inverse matrix.
```{r}
f$getinverse();
```

